Enhancement of SDR in Thessaloniki

### 2024-03-01 GHI_enh_04_investigate.tex
Commit 2024-02-29 19:12
Commit 2024-02-29 20:15
Commit 2024-03-01 19:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-02-29}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\begin{verbatim}
2024-02-29 16:10:43.9 athan@tyler GHI_enh_04_investigate.R 1.399842 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-01}

@@

\begin{verbatim}
Warning in ans * length(l) + if1: longer object length is not a multiple of
shorter object length
\end{verbatim}

@@

lmD: 0.9508227 +/- 0.1552488

lmY: 0.9508465 +/- 0.1552515

Arima: 1.0223 0.2369 4.315 0

@@

lmD: 0.001714795 +/- 0.0002777698

lmY: 0.001714851 +/- 0.0002777746

Arima: 0.0019 5e-04 4.0604 0

@@

lmD: 0.2160878 +/- 0.03807227

lmY: 0.2160919 +/- 0.03807295

Arima: 0.2161 0.0414 5.2173 0

@@

lmD: 0.000422753 +/- 5.903214e-05

lmY: 0.0004227591 +/- 5.903319e-05

Arima: 4e-04 1e-04 6.291 0

@@

lmD: 0.0498083 +/- 0.192504

lmY: 0.04983275 +/- 0.1925071

Arima: 0.0086 0.3464 0.0248 0.9802

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-25} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-26} \end{center}

lmD: 0.0003565528 +/- 0.0002141263

lmY: 0.0003565519 +/- 0.0002141297

Arima: 3e-04 3e-04 1.3206 0.1866

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-27} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-28} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-29} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-30} \end{center}

@@

\begin{verbatim}
2024-03-01 16:24:25.3 athan@tyler GHI_enh_04_investigate.R 1.012841 mins
\end{verbatim}
